### 2014-04-13 patchy-selection-paper.tex
.

% \newcommand{\var}{\mathop{\mbox{Var}}}
% \newcommand{\Exp}{\mathop{\mbox{Exp}}}
\DeclareMathOperator{\var}{Var}
\DeclareMathOperator{\Exp}{Exp}
\DeclareMathOperator{\sn}{sn}
\renewcommand{\P}{\mathbb{P}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\calE}{\mathcal{E}}
\newcommand{\calC}{\mathcal{C}}
\newcommand{\dconv}{\xrightarrow{d}}
\newcommand{\deq}{\stackrel{\scriptscriptstyle{d}}{=}}

@@

We can understand this quite concretely, by a method described rigorously by \citet{geiger1999elementary}.
When we condition on survival until $t$, we condition on existence of at least one lineage surviving from time $0$ to time $t$.
Once given this lineage, nothing distinguishes any of the other reproduction events --
each individual in this lineage must give birth to at least one offspring,
and all other reproduction events are unconditioned.
In other words, the genealogy of a family that survives until $t$
can be decomposed into a ``trunk'' that lasts until $t$
which sprouts independent ``branches'' that may or may not survive until $t$.
This process is depicted in Figure~\ref{fig:branching_decomp}A.
Concretely, if we write $Z_t$ for the number of offspring in the branching process alive at time $t$,
% (so $\P\{Z_t = 0\} = p_e(t)$),
then this gives the following decomposition:
\begin{align}
  \left( Z_t \; \vert \; Z_t>0 \right) \deq \sum_{s=0}^t \sum_{k=1}^{W_s-1} Z^{(s,k)}_{t-s},
\end{align}
where each $Z^{(s,k)}$ is an independent copy of $Z$,
and each $W_s$ is an independent copy of the offspring distribution, conditioned on $W_s \ge 1$.

@@

>>>>

% \newcommand{\var}{\mathop{\mbox{Var}}}
% \newcommand{\Exp}{\mathop{\mbox{Exp}}}
\DeclareMathOperator{\var}{Var}
\DeclareMathOperator{\Exp}{Exp}
\DeclareMathOperator{\sn}{sn}
\renewcommand{\P}{\mathbb{P}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\one}{\mathbb{1}}
\newcommand{\calE}{\mathcal{E}}
\newcommand{\calC}{\mathcal{C}}
\newcommand{\dconv}{\xrightarrow{d}}
\newcommand{\deq}{\stackrel{\scriptscriptstyle{d}}{=}}

@@

We can understand this quite concretely, by a method described rigorously by \citet{geiger1999elementary} \citep[see also][]{chauvin1991growing}.
When we condition on survival until $t$, we condition on existence of at least one lineage surviving from time $0$ to time $t$.
Once given this lineage, nothing distinguishes any of the other reproduction events --
each individual in this lineage must give birth to at least one offspring,
and all other reproduction events are unconditioned.
In other words, the genealogy of a family that survives until $t$
can be decomposed into a ``trunk'' that lasts until $t$
which sprouts independent ``branches'' that may or may not survive until $t$.
This process is depicted in Figure~\ref{fig:branching_decomp}A.
Concretely, if we write $Z_t$ for the number of offspring in the branching process alive at time $t$,
% (so $\P\{Z_t = 0\} = p_e(t)$),
then this gives the following decomposition:
\begin{align}
  \left( Z_t \; \vert \; Z_t>0 \right) \deq \sum_{s=0}^t \sum_{k=1}^{W_s-1} Z^{(s,k)}_{t-s},
\end{align}
where each $Z^{(s,k)}$ is an independent copy of $Z$,
and each $W_s$ is an independent copy of the offspring distribution, conditioned on $W_s \ge 1$.

@@

Now note that if $\tau$ is Exponential($\alpha$), then
\begin{align}
  q(y) &= \frac{1}{\alpha} \int_{\partial B} \E^x[ \int_0^\tau \one_A(B_t) dt ] dx 
\end{align}
and that if $\mu(x,A)$ is the hitting distribution of $\partial A$ by $B_{t \min \tau}$,
\begin{align}
  \E^x[ \int_0^\tau \one_A(B_t) dt ] &= \P^x\{ \tau_A < \tau \}  \E^{\mu(x,A)}[ \int_0^\tau \one_A(B_t) dt ] .
\end{align}
If $A$ is circular, then the latter term is the integral of the Green function, so using Borodin \& Salminen (Appendix 1),
in $d=1$,
\begin{align}
  \E^w[ \int_0^\tau \one_A(B_t) dt ] &= \alpha \int_0^{2w} G_\alpha(0,y) dy \\
  &= \alpha \int_0^{2w} \frac{ e^{- y \sqrt{2\alpha} }}{2\sqrt{2\alpha}} dy
\end{align}
and in $d=2$,
\begin{align}
  \E^w[ \int_0^\tau \one_A(B_t) dt ] &= \alpha \int_0^{2w} G_\alpha(0,y) dy \\
  &= \alpha \int_0^{2w} K_0(y \sqrt{2\alpha}) dy 
\end{align}
